\Title

### 2022-09-23 Grimaldi-etal-BiolCybernetics.tex
Methods: 1a

\subsection{A generative model for raster plots}

@@

For any generic raster plot, such as the sensory signal representing the output of an event-based camera, consists a stream of events (see Figure~\ref{fig:model}-(a)). This can be formalized as an ordered set of addresses and timestamps: $\event = \{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event $\event_\arank$. That event has a time of occurrence $\timev_\arank$  and an associated address, which is typically in the form $\presynaddr_\arank=(x_\arank, y_\arank, \polev_\arank)$. This defines a presynaptic address space $\presynaddrspace$ which in the particular case of event-based cameras is denoted by $[1, \Nx]\times[1, \Ny] \times [1, \Npol] \subset \mathbb{N}^3$ where $(\Nx, \Ny)$ is the size of the sensor in pixels and $\Npol$ is the number of polarities ($\Npol=2$ for ON and OFF polarities). 
In general, a spiking neuron is defined on the one hand by the equations governing the evolution of its membrane potential dynamics on its soma and on the other hand by the characterization of the synaptic contacts on its dendritic tree. A classical characterization consists in detailing the synaptic weights of each synaptic contact on the dendritic tree. A more detailed examination of these synaptic contacts reveals the added importance of hetero-synaptic delays, i.e., the precise timing from synaptic activation to its integration into the soma, and how this changes the network's dynamics~\citep{Izhikevich06}. Thus, we can parameterize each neuron by the set of tuples defining the weight and delay of each synaptic contact. 
The corresponding set of input presynaptic spikes $\event$ will be integrated by this synaptic set and notably by the respective delays, which will multiplex in time all possible motifs. For each time $\timev$ the integration of $\event$ is defined by a list of weights $\activeweights^\postsynaddr$ linked to the synapses that match a precise spatio-temporal motif as input:
\begin{equation*}
\activeweights^\postsynaddr (t) = 
\{ \synapticweight_\ranksyn^\postsynaddr  \vert 
\presynaddr_\arank = 
 \presynaddr_\ranksyn^\postsynaddr \; \text{and} \; \timev=\timev_\arank + 
\synapticdelay_\ranksyn^\postsynaddr \}_{ \arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]} 
\}
\end{equation*}

When a neuron is activated by a discharge motif that corresponds to this specific set of delays and addresses, the discharge probability will increase. Following the observations of~\citet{Izhikevich06}, let us assume that such precise discharge motif defines a polychronous group (PG). Assuming that we know there exists $M$ such groups, we will define as $b \in [1, M]$ the address of a PG and as $W_b$ the corresponding weight matrices. This allows then to derive a generative model for raster plots (see Figure~\ref{fig:1}).

%: Detection model
Let's first define a layer of hetero-synaptic spiking neurons $\postsynaddr \in \postsynaddrspace$ by first describing how each neuron connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses, and each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact an afferent neuron with multiple different delays. For each neuron $\postsynaddr$, we thus define a set of $\Nsyn^\postsynaddr$ synapses, as  $\synapse^\postsynaddr = \{(\presynaddr^\postsynaddr_\ranksyn, \synapticweight^\postsynaddr_\ranksyn, \synapticdelay^\postsynaddr_\ranksyn)\}_{\ranksyn \in [1,\Nsyn^\postsynaddr]}$, where each synapse $\synapse^\postsynaddr_\ranksyn$ is associated to a weight $\synapticweight^\postsynaddr_\ranksyn$, a delay $\synapticdelay^\postsynaddr_\ranksyn$ and a presynaptic address $\presynaddr^\postsynaddr_\ranksyn$. This defines the full connectivity of the hetero-synaptic model.

@@

Indeed, the probability of firing of a neuron $a$ at a given time $t$ can be understood as a Bernoulli trial whose (only) parameter is a bias $p(t, a) \in [0, 1]$. Assuming that the presence of PGs is conditionally independent, this bias can be written as the combination of these factors, whose values are given by the corresponding weights. PGs may be activated independently at random times and  we write that $B(b, t)=1$ if $b$ is activated at $t$ (and else $B(b, t)=0$). We can thus write the probability bias as the accumulated evidence given these factors as 
\begin{equation*}
p(t, a) = \sigma\big(W_0 + \sum_{b, t} B(b, t) \cdot W_b(a, t-d) \big)  
\end{equation*}
where $\sigma$ is the sigmoid function. We will further assume that the weights are balanced (their mean is zero) and that $W_0$ is a bias such that $p_0=\sigma(W_0)$ is the average background firing rate. Conveniently, one can write this summation as a one-dimensional temporal convolution operator such that we may simply write $p = \sigma(W_0 + B \ast W )$ where  $p\in [ 0, 1]^{N\times T}$ and $B\in \{0, 1\}^{M\times T}$ is the raster plot corresponding to the temporal activation of the PGs. Finally, we obtain the raster plot $A\in \{0, 1\}^{N\times T}$ by drawing spikes using independent Bernoulli trials $A \sim \mathcal{B}(p)$. Note that, depending on the shape of the kernels, the generative model can model a Poisson process, generate rhythmic activity or more generally propagating waves. This formulation thus defines a simple generative model for raster plots as a combination of independent PGs.

%The activation function of our spiking neuron is a softmax function implementing a form of  Multinomial Logistic Regression (MLR)~\cite{Grimaldi22pami}, in analogy to a spiking Winner-Take-All network~\cite{nessler2013bayesian}. It transforms this list of weights into a probability with the following formula:
%$
%Pr(k=\postsynaddr \; | \; \timev) =
%\frac 1 Z
%{\exp  (\mathcal{C}^\postsynaddr(\timev) +\bias^\postsynaddr) }
%$ 
%where $\mathcal{C}^\postsynaddr(\timev) = \sum
%\activeweights^\postsynaddr(t)
%$ is the sum of the synaptic weights and $\bias^\postsynaddr$ is the bias linked to neuron $\postsynaddr$. 
%In particular, some specific motifs may become tightly synchronized as they reach the basal dendritic tree, leading to a high postsynaptic activity which makes it progressively more likely to generate an output spike.
%
We may now define a layer of neurons $\postsynaddr \in \postsynaddrspace$ by first describing how each neuron connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses, and each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then not only described by synaptic weights connecting to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. For each neuron $\postsynaddr$, we define a set of $\Nsyn^\postsynaddr$ synapses, as  $\synapse^\postsynaddr = \{(\presynaddr^\postsynaddr_\ranksyn, \synapticweight^\postsynaddr_\ranksyn, \synapticdelay^\postsynaddr_\ranksyn)\}_{\ranksyn \in [1,\Nsyn^\postsynaddr]}$, where each synapse $\synapse^\postsynaddr_\ranksyn$ is associated to a weight $\synapticweight^\postsynaddr_\ranksyn$, a delay $\synapticdelay^\postsynaddr_\ranksyn$ and a presynaptic address $\presynaddr^\postsynaddr_\ranksyn$. Note that a neuron may contact an afferent neuron with multiple, different delays.

@@

The activation function of our spiking neuron is a softmax function implementing a form of  Multinomial Logistic Regression (MLR)~\citep{grimaldi_robust_2022}, in analogy to a spiking Winner-Take-All network~\citep{nessler_bayesian_2013}. 
It transforms this list of weights into a probability with the following formula:
$
Pr(k=\postsynaddr \; \vert \; \timev) =
\frac 1 Z
{\exp  (\mathcal{C}^\postsynaddr(\timev) +\bias^\postsynaddr) }
$ 
where $\mathcal{C}^\postsynaddr(\timev) = \sum
\activeweights^\postsynaddr(t)
$ is the sum of the synaptic weights and $\bias^\postsynaddr$ is the bias linked to neuron $\postsynaddr$. 
In particular, we expect that some specific motifs may become tightly synchronized as they reach the basal dendritic tree, leading to a high postsynaptic activity which makes it progressively more likely to generate an output spike.
%
%In our MLR model with $\Nclass=\Nspeed$ classes, a probability value is predicted for each event at address $\presynaddr_\arank$ and at time $\timev_\arank$ as a softmax function of the linear combination of the list of events on the basal dendrite of a neuron $\postsynaddr$ in association to a specific class. The linear combination can be defined by a set of synapses $\synapse^\postsynaddr$ as described in the hetero-synaptic delays model. 
%
%
In our MLR model with $\Nclass=\Nspeed$ classes, 
a probability value is predicted for each event at address $\presynaddr_\arank$ and at time $\timev_\arank$ as a softmax function of the linear combination of the list of events on the basal dendrite of a neuron $\postsynaddr$ in association to a specific class. 
The linear combination can be defined by a set of synapses $\synapse^\postsynaddr$ as described in the hetero-synaptic delays model. 
%
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.490\linewidth]{figures/figure_N_PGs.pdf}
    \includegraphics[width=0.490\linewidth]{figures/figure_N_PG_time.pdf}
	    \caption{Detecting event-based motifs using spiking neurons with hetero-synaptic delays. 
	    {\bf (a)}~Accuracy of PG detection as a function of the number $M$ of kernels.
	    {\bf (b)}~Accuracy of PG detection as a function of the temporal depth $D$ of kernels.
	    	     }
    \label{fig:model_results}
\end{figure}
%

This generative model defined above allows to determine this inference model for guessing sources $B$ when observing a raster plot $A$. This assumes that we know the PGs as defined by the $W_b$ matrices. The underlying metric is the binary cross-entropy, as used in the logistic regression model. In particular, if we consider PG kernels with similar decreasing exponential time profile, we can prove that this is similar to the method of~\citet{berens_fast_2012}. In our specific case, the difference is that the regression is performed in both dendritic and delay space by extending the summation using a temporal convolution operator. Using this forward model, it possible to estimate the logit (inverse of a sigmoid) $\hat{B}(b, t)$ for the presence of a PG of address $b$ and at time $t$ by using the transpose convolution operator. It thus comes that when observing $A$, then one may infer $\hat{B} = A \ast W^T$ and select the most activated items. To quantify the efficiency of this operation, we generated $M=55$ synthetic PGs as random independent kernels over $128$ presynaptic inputs and $D=127$ possible delays. We drew random independent instances of $B$ with a length of $T=1000$ time steps and with on average $2.0$ occurrences each. This allowed us to generate raster plots which we use to infer $\hat{B}$. We compute the accuracy as the rate of true positive detections (both for inferring the address and its exact timing) and observe on average $\approx 98\%$ correct detections. We further extended this result by showing how the accuracy would evolve as a function of the number of simultaneous PGs, while keeping the same frequency of occurrence. We show in Figure~\ref{fig:model_results}~(a) that the accuracy of finding the right PG is still above $80\%$ accuracy with more than $1364$ overlapping PGs. Moreover, we show in Figure~\ref{fig:model_results}~(b) that (with $M=55$ PGs fixed) the accuracy increases notably as the temporal depth $D$ of the PG kernel increased, demonstrating quantitatively the potential of hetero-synaptic delays. These results were obtained while assuming that we know $W$. However, this is in general not the case, for instance when observing the raster plot of a population of neurons. In the following, we will define a generic visual task and determine a learning algorithm to solve it. %Inspired by the k-means algorithm, it is possible to devise a self-supervised learning algorithm. Our preliminary results show that it is possible to retrieve PGs embedded in the data, yet that further analysis is necessary to improve the convergence of the algorithm. In particular, it seems promising to use a sparseness constraint in the inference mechanism such as to remove spurious correlations in the inference.

>>>>

\subsubsection{A generative model for raster plots}

@@

As in a neurobiological recording, or in the sensory signal representing the output of an event-based camera,  any generic raster plot consists a stream of spikes (see Figure~\ref{fig:model}-(a)). This can be formalized as an ordered set of addresses and timestamps: $\event = \{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event $\event_\arank$. That event has a time of occurrence $\timev_\arank$  and an associated address (which is typically in the form $\presynaddr_\arank=(x_\arank, y_\arank, \polev_\arank)$ for event-based cameras). This defines an address space $\presynaddrspace$ which consists the identified set of neurons in the neurobiological recording, or is denoted for event-based cameras by $[1, \Nx]\times[1, \Ny] \times [1, \Npol] \subset \mathbb{N}^3$ where $(\Nx, \Ny)$ is the size of the sensor in pixels and $\Npol$ is the number of polarities ($\Npol=2$ for ON and OFF polarities).

A spiking neuron is defined on the one hand by the equations governing the evolution of its membrane potential dynamics on its soma and on the other hand by the characterization of the synaptic contacts on its dendritic tree. A classical characterization consists in detailing the synaptic weights of each synaptic contact on the dendritic tree, the so-called weight matrix. A more detailed description of these synaptic contacts reveals the added importance of hetero-synaptic delays, i.e., the precise timing from synaptic activation to its integration into the soma, and how this changes the network's dynamics~\citep{Izhikevich06}. In that hetero-synaptic description, we can parameterize each neuron by the set of tuples defining the weight and delay of each synaptic contact. As a consequence, a set of input presynaptic spikes $\event$ will be processed by the dendrite defined by this synaptic set and notably by the respective delays, which will multiplex in time all events.

Let's first define a layer of hetero-synaptic spiking neurons $\postsynaddr \in \postsynaddrspace$ by first describing how each neuron connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses, and each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact an afferent neuron with multiple different delays. For each neuron $\postsynaddr$, we thus define a set of $\Nsyn^\postsynaddr$ synapses, as  $\synapse^\postsynaddr = \{(\presynaddr^\postsynaddr_\ranksyn, \synapticweight^\postsynaddr_\ranksyn, \synapticdelay^\postsynaddr_\ranksyn)\}_{\ranksyn \in [1,\Nsyn^\postsynaddr]}$, where each synapse $\synapse^\postsynaddr_\ranksyn$ is associated to a weight $\synapticweight^\postsynaddr_\ranksyn$, a delay $\synapticdelay^\postsynaddr_\ranksyn$ and a presynaptic address $\presynaddr^\postsynaddr_\ranksyn$. This defines the full connectivity of the hetero-synaptic model.

Formally, for each time $\timev$ the integration of $\event$ is defined by a list of weights $\activeweights^\postsynaddr$ linked to the synapses that match a precise spatio-temporal motif as input:
\begin{equation*}
\activeweights^\postsynaddr (t) = 
\{ \synapticweight_\ranksyn^\postsynaddr  \vert 
\presynaddr_\arank = 
 \presynaddr_\ranksyn^\postsynaddr \; \text{and} \; \timev=\timev_\arank + 
\synapticdelay_\ranksyn^\postsynaddr \}_{ \arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]} 
\}
\end{equation*}

This raster plot is generated either by a event generation process or by other spiking neurons.

When a neuron is activated by a discharge motif that corresponds to this specific set of delays and addresses, the discharge probability will increase. Following the observations of~\citet{Izhikevich06}, let us assume that such precise discharge motif defines a polychronous group (PG). Assuming that we know there exists $M$ such groups, we will define as $b \in [1, M]$ the address of a PG and as $W_b$ the corresponding weight matrices. This allows then to derive a generative model for raster plots (see Figure~\ref{fig:model}-(b)).

\subsubsection{Detecting spiking motifs}
%: Detection model

@@

Indeed, the probability of firing of a neuron $a$ at a given time $t$ can be understood as a Bernoulli trial whose (only) parameter is a bias $p(t, a) \in [0, 1]$. Assuming that the presence of PGs is conditionally independent, this bias can be written as the combination of these factors, whose values are given by the corresponding weights. PGs may be activated independently at random times and  we write that $B(b, t)=1$ if $b$ is activated at $t$ (and else $B(b, t)=0$). We can thus write the probability bias as the accumulated evidence given these factors as 
\begin{equation*}
p(t, a) = \sigma\big(W_0 + \sum_{b, t} B(b, t) \cdot W_b(a, t-d) \big)  
\end{equation*}
where $\sigma$ is the sigmoid function. We will further assume that the weights are balanced (their mean is zero) and that $W_0$ is a bias such that $p_0=\sigma(W_0)$ is the average background firing rate. Conveniently, one can write this summation as a one-dimensional temporal convolution operator such that we may simply write
\begin{equation*}
p = \sigma(W_0 + B \ast W )
\end{equation*}
where  $p\in [ 0, 1]^{N\times T}$ and $B\in \{0, 1\}^{M\times T}$ is the raster plot corresponding to the temporal activation of the PGs. Finally, we obtain the raster plot $A\in \{0, 1\}^{N\times T}$ by drawing spikes using independent Bernoulli trials $A \sim \mathcal{B}(p)$. Note that, depending on the shape of the kernels, the generative model can model a Poisson process, generate rhythmic activity or more generally propagating waves. This formulation thus defines a simple generative model for raster plots as a combination of independent PGs.

\subsubsection{Implementation using spiking neurons with hetero-synaptic delays}
%
%The activation function of our spiking neuron is a softmax function implementing a form of  Multinomial Logistic Regression (MLR)~\cite{Grimaldi22pami}, in analogy to a spiking Winner-Take-All network~\cite{nessler2013bayesian}. It transforms this list of weights into a probability with the following formula:
%$
%Pr(k=\postsynaddr \; | \; \timev) =
%\frac 1 Z
%{\exp  (\mathcal{C}^\postsynaddr(\timev) +\bias^\postsynaddr) }
%$ 
%where $\mathcal{C}^\postsynaddr(\timev) = \sum
%\activeweights^\postsynaddr(t)
%$ is the sum of the synaptic weights and $\bias^\postsynaddr$ is the bias linked to neuron $\postsynaddr$. 
%In particular, some specific motifs may become tightly synchronized as they reach the basal dendritic tree, leading to a high postsynaptic activity which makes it progressively more likely to generate an output spike.
%
We may now define a layer of neurons $\postsynaddr \in \postsynaddrspace$ by first describing how each neuron connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses, and each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then not only described by synaptic weights connecting to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. For each neuron $\postsynaddr$, we define a set of $\Nsyn^\postsynaddr$ synapses, as  $\synapse^\postsynaddr = \{(\presynaddr^\postsynaddr_\ranksyn, \synapticweight^\postsynaddr_\ranksyn, \synapticdelay^\postsynaddr_\ranksyn)\}_{\ranksyn \in [1,\Nsyn^\postsynaddr]}$, where each synapse $\synapse^\postsynaddr_\ranksyn$ is associated to a weight $\synapticweight^\postsynaddr_\ranksyn$, a delay $\synapticdelay^\postsynaddr_\ranksyn$ and a presynaptic address $\presynaddr^\postsynaddr_\ranksyn$. Note that a neuron may contact an afferent neuron with multiple, different delays.

@@

The activation function of our spiking neuron is a softmax function implementing a form of  Multinomial Logistic Regression (MLR)~\citep{grimaldi_robust_2022}, in analogy to a spiking Winner-Take-All network~\citep{nessler_bayesian_2013}. 
It transforms this list of weights into a probability with the following formula:
$
Pr(k=\postsynaddr \; \vert \; \timev) =
\frac 1 Z
{\exp  (\mathcal{C}^\postsynaddr(\timev) +\bias^\postsynaddr) }
$ 
where $\mathcal{C}^\postsynaddr(\timev) = \sum
\activeweights^\postsynaddr(t)
$ is the sum of the synaptic weights and $\bias^\postsynaddr$ is the bias linked to neuron $\postsynaddr$. 
In particular, we expect that some specific motifs may become tightly synchronized as they reach the basal dendritic tree, leading to a high postsynaptic activity which makes it progressively more likely to generate an output spike.
%
%In our MLR model with $\Nclass=\Nspeed$ classes, a probability value is predicted for each event at address $\presynaddr_\arank$ and at time $\timev_\arank$ as a softmax function of the linear combination of the list of events on the basal dendrite of a neuron $\postsynaddr$ in association to a specific class. The linear combination can be defined by a set of synapses $\synapse^\postsynaddr$ as described in the hetero-synaptic delays model. 
%
%
In our MLR model with $\Nclass=\Nspeed$ classes, 
a probability value is predicted for each event at address $\presynaddr_\arank$ and at time $\timev_\arank$ as a softmax function of the linear combination of the list of events on the basal dendrite of a neuron $\postsynaddr$ in association to a specific class. 
The linear combination can be defined by a set of synapses $\synapse^\postsynaddr$ as described in the hetero-synaptic delays model.

\subsubsection{Performance on synthetic data}
%
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.490\linewidth]{figures/figure_N_PGs.pdf}
    \includegraphics[width=0.490\linewidth]{figures/figure_N_PG_time.pdf}
	    \caption{Detecting event-based motifs using spiking neurons with hetero-synaptic delays. 
	    {\bf (a)}~Accuracy of PG detection as a function of the number $M$ of kernels.
	    {\bf (b)}~Accuracy of PG detection as a function of the temporal depth $D$ of kernels.
	    	     }
    \label{fig:model_results}
\end{figure}
%

This generative model defined above allows to determine this inference model for guessing sources $B$ when observing a raster plot $A$. This assumes that we know the PGs as defined by the $W_b$ matrices. The underlying metric is the binary cross-entropy, as used in the logistic regression model. In particular, if we consider PG kernels with similar decreasing exponential time profile, we can prove that this is similar to the method of~\citet{berens_fast_2012}. In our specific case, the difference is that the regression is performed in both dendritic and delay space by extending the summation using a temporal convolution operator. Using this forward model, it possible to estimate the logit (inverse of a sigmoid) $\hat{B}(b, t)$ for the presence of a PG of address $b$ and at time $t$ by using the transpose convolution operator. It thus comes that when observing $A$, then one may infer $\hat{B} = A \ast W^T$ and select the most activated items.

To quantify the efficiency of this operation, we generated $M=55$ synthetic PGs as random independent kernels over $128$ presynaptic inputs and $D=127$ possible delays. We drew random independent instances of $B$ with a length of $T=1000$ time steps and with on average $2.0$ occurrences each. This allowed us to generate raster plots which we use to infer $\hat{B}$. We compute the accuracy as the rate of true positive detections (both for inferring the address and its exact timing) and observe on average $\approx 98\%$ correct detections. We further extended this result by showing how the accuracy would evolve as a function of the number of simultaneous PGs, while keeping the same frequency of occurrence. We show in Figure~\ref{fig:model_results}~(a) that the accuracy of finding the right PG is still above $80\%$ accuracy with more than $1364$ overlapping PGs. Moreover, we show in Figure~\ref{fig:model_results}~(b) that (with $M=55$ PGs fixed) the accuracy increases notably as the temporal depth $D$ of the PG kernel increased, demonstrating quantitatively the potential of hetero-synaptic delays. These results were obtained while assuming that we know $W$. However, this is in general not the case, for instance when observing the raster plot of a population of neurons. In the following, we will define a generic visual task and determine a learning algorithm to solve it. %Inspired by the k-means algorithm, it is possible to devise a self-supervised learning algorithm. Our preliminary results show that it is possible to retrieve PGs embedded in the data, yet that further analysis is necessary to improve the convergence of the algorithm. In particular, it seems promising to use a sparseness constraint in the inference mechanism such as to remove spurious correlations in the inference.
